「赴尘杯」2025 年普通高中学业水平选择性考试适应性演练

### 2025-01-20 Dustbound/English/Dustbound_English_I/paper.tex
feat: :sparkles: 英语 I 七选五题目完成~

\examsetup{
  page = {
    foot-content = 「赴尘杯」英语试题第 ; 页（共 ; 页）
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

@@

The universal appeal of these tales is frequently attributed to the idea that they contain cautionary messages: in the case of \textit{Little Red Riding Hood}, to listen to your mother, and avoid talking to strangers. ``It might be what we find interesting about this story is that it's got this survival relevant information in it,'' says anthropologist Jamie Tehrani at Durham University in the UK. But his research suggests otherwise. ``We have this huge gap in our knowledge about the history and prehistory of storytelling, despite the fact that we know this genre is an incredibly ancient one,'' he says. That hasn't stopped anthropologists, folklorists and other academics devising theories to explain the importance of fairy tales in human society. Now Tehrani has found a way to test these ideas, borrowing a technique from evolutionary biologists.

@@

First he tested some assumptions about which aspects of the story alter least as it evolves, indicating their importance. Folklorists believe that what happens in a story is more central to the story than the characters in it—that visiting a relative, only to be met by a scary animal in disguise, is more fundamental than whether the visitor is a little girl or three siblings, or the animal is a tiger instead of a wolf.

@@

The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all. Why are these details retained by generations of storytellers, when other features are not? Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller. \fillin[A]'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.

Jack Zipes at the University of Minnesota, Minneapolis, is unconvinced by Tehrani's views on fairy tales. ``Even if they're gruesome, they won't stick unless they matter,'' he says. He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant. But Tehrani points out that although this is often the case in Western versions, it is not always true elsewhere. In Chinese and Japanese versions, often known as \textit{The Tiger Grandmother}, the villain is a woman, and in both Iran and Nigeria, the victim is a boy.

@@

\begin{choices}
\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller.
\end{choices}

>>>>

\examsetup{
  page = {
    foot-content = 「赴尘杯」英语试题第 ; 页（共 ;页）
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

@@

The universal appeal of these tales is frequently attributed to the idea that they contain cautionary messages: in the case of \textit{Little Red Riding Hood}, to listen to your mother, and avoid talking to strangers. ``It might be what we find interesting about this story is that it's got this survival relevant information in it,'' says anthropologist Jamie Tehrani at Durham University in the UK. \fillin[A]. ``We have this huge gap in our knowledge about the history and prehistory of storytelling, despite the fact that we know this genre is an incredibly ancient one,'' he says. That hasn't stopped anthropologists, folklorists and other academics devising theories to explain the importance of fairy tales in human society. Now Tehrani has found a way to test these ideas, borrowing a technique from evolutionary biologists.

@@

First he tested some assumptions about which aspects of the story alter least as it evolves, indicating their importance. \fillin[D]—that visiting a relative, only to be met by a scary animal in disguise, is more fundamental than whether the visitor is a little girl or three siblings, or the animal is a tiger instead of a wolf.

@@

The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all. \fillin[B]? Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller. \fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.

Jack Zipes at the University of Minnesota, Minneapolis, is unconvinced by Tehrani's views on fairy tales. ``Even if they're gruesome, they won't stick unless they matter,'' he says. \fillin[F]. But Tehrani points out that although this is often the case in Western versions, it is not always true elsewhere. In Chinese and Japanese versions, often known as \textit{The Tiger Grandmother}, the villain is a woman, and in both Iran and Nigeria, the victim is a boy.

@@

\begin{choices}
\item But his research suggests otherwise
\item Why are these details retained by generations of storytellers, when other features are not
\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller
\item Folklorists believe that what happens in a story is more central to the story than the characters in it
\item According to folklorists, the impression left by a story’s characters tends to be stronger than that of the events unfolding within it
\item He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant
\item He holds the point that fairy tales continue to be passed down through generations because they frequently depict women as storytellers
\end{choices}
